Exploring the tree of numerical semigroups

### 2013-10-08 Papier/article.tex
Florent's rant

\section{Technical optimizations and results}
\label{S:Opti}

>>>>

\section{Technical optimizations and results}

Though there are asymptotically faster algorithm than the one presented here,
thank to careful optimizations, we were able to compute $n_g$ for much larger
genus than before. This is due to the fact that our algorithm is very well
suited for the current processor architecture. In particular, it allows to use
parallelism at various scale (parallel branch exploration, vectorization)...

\subsection{Florent's rant}

We use the following optimization tricks
\begin{itemize}
\item Vectorisation (MMX, SSE, GCC's 
\verb|__attribute__ ((vector_size(16)));|
) and careful memory alignment.
\item Shared memory multicore computing using \texttt{CILK++} for low level
  enumerating tree branching;
\item Un-recursived algorithm using a stack;
\item Avoiding all dynamic allocation during the computation: everything is
  computed ``in place'';
\item Avoiding all unnecessary copy (the cost of the \textsc{Son} algorithm is
  roughly the same (even less) as for as copy !
\item Aggressive loop unrolling. The main loop is unrolled by hand using some
  kind of Duff's device.
\item Carefull choice of data type (\verb|uint_fast8_t| for decomposition
  number, vs \verb|uint_fast64_t| for all indexes).
\end{itemize}

\label{S:Opti}
